Matching Bullets

### 2015-12-10 imaging-paper.Rnw
Clean up section introducing loess.

Next, we fit a Loess regression to the data. Figure \ref{fig:loess_fit} provides a look at the Loess fit, in blue, overlaid against the processed image of part 1 of bullet 1. The fit seems to do a reasonable job of capturing the structure of the image. Figure \ref{fig:loess_resid} shows the residuals from this fit. 
\hh{XXX what purpose does the next paragraph have? I think you just want end this section, but it brings up two new ideas: autocorrelation and dependency on the span. The span obviously doesn't get any resolution ... so it's just muddying the waters at the moment ... XXX}
It is clear that there is a rather significant amount of autocorrelation, which make sense given the presence of striations and markings. Certainly, tuning the parameters for this regression, such as the Loess span, could prove to do an even better job at making the markings more clear. \hh{XXX did you follow up on that? What is the effect of using a different span?}

@@

We can reproduce a similar figure to the one from the circular fits by overlaying the residuals from each loess fit for bullet 2 onto an image of the loess residuals from bullet 1-5. This is shown in Figure~\ref{fig:loessfits}. \hh{The first land of bullet 2 is still the best  match for land 5, but now the details of the match are more pronounced.}

>>>>

Next, we fit a Loess regression to the data. Figure \ref{fig:loess_fit} provides a look at the Loess fit, in blue, overlaid against the processed image of part 1 of bullet 1. The fit seems to do a reasonable job of capturing the structure of the image. Figure \ref{fig:loess_resid} shows the residuals from this fit. We can reproduce a similar figure to the one from the circular fits by overlaying the residuals from each loess fit for bullet 2 onto an image of the loess residuals from bullet 1-5. This is shown in Figure~\ref{fig:loessfits}. Bullet 2-1 is still the best match for bullet 1-5, but now the details of the match are more pronounced.

@@
